---
title: "Lab 3"
author: "Greycin Kim"
date: "2024-09-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Quantitative Data Variables
The two variables I collected in class are:

1. Units Enrolled This Semester
2. Number of TV Shows Currently Watching

# Units Enrolled This Semester
```{r unitsTakenVector, echo = TRUE}
unitsTakenVector = c(15, 11, 13, 14, 14, 13, 16, 14, 16, 15)

meanUnitsTaken = mean(unitsTakenVector)
modeUnitsTaken = 14
medianUnitsTaken = median(unitsTakenVector)
rangeUnitsTaken = diff(range(unitsTakenVector))
SDUnitsTaken = sd(unitsTakenVector)

Q1 <- quantile(unitsTakenVector, 0.25)
Q3 <- quantile(unitsTakenVector, 0.75)
IQR <- Q3 - Q1

lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR
```
The mean is: `r meanUnitsTaken`

The mode is: `r modeUnitsTaken`

The median is: `r medianUnitsTaken`

The range is: `r rangeUnitsTaken`

The Standard Deviation is: `r SDUnitsTaken`

Q1 is `r Q1` and Q2 is `r Q3` and the IQR is `r IQR`

lowerbound is `r lower_bound` and the upperbound is `r upper_bound`. Therefore the outliers are 11



# Number of TV Shows Currently Watching
```{r numOfTVShows, echo=TRUE}
numOfTVShowsCurrentlyWatching = c(1, 2, 2, 0, 3, 1, 1, 9, 1, 2)

meanNumOfTVShows = mean(numOfTVShowsCurrentlyWatching)
modeNumOfTVShows = 1
medianNumOfTVShows = median(numOfTVShowsCurrentlyWatching)
rangeNumOfTVShows = diff(range(numOfTVShowsCurrentlyWatching))
SDNumOfTVShows = sd(numOfTVShowsCurrentlyWatching)

Q1 <- quantile(numOfTVShowsCurrentlyWatching, 0.25)
Q3 <- quantile(numOfTVShowsCurrentlyWatching, 0.75)
IQR <- Q3 - Q1

lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR
```

The mean is: `r meanNumOfTVShows`

The mode is: `r modeNumOfTVShows`

The median is: `r medianNumOfTVShows`

The range is: `r rangeNumOfTVShows`

The Standard Deviation is: `r SDNumOfTVShows`

Q1 is `r Q1` and Q2 is `r Q3` and the IQR is `r IQR`

lowerbound is `r lower_bound` and the upperbound is `r upper_bound`. Therefore the outliers is 9


# Histogram of Number of Tv Shows class is currently watching
```{r hist, echo=TRUE}
numOfTVShowsCurrentlyWatching = c(1, 2, 2, 0, 3, 1, 1, 9, 1, 2)

hist(numOfTVShowsCurrentlyWatching)
```

The shape is right skewed because the majority of the values are concentrated on the left side of the histogram and there is a long tail extending to the right
